Another paper with lots of text and fancy pictures

### 2023-11-09 paper.tex
Rotations! Rotations!

\textcolor{red}{Where to put this?}
We have made a comparison of our algorithm with two algorithms, one of which
proposed by Malmir~et~al \cite{malmir2018} and another proposed by Smith and
Torquato \cite{SMITH1988176}. The first algorithms generates a triangle with
fixed sides $r_1$ and $r_2$ and an angle $\theta$ between them and places it in
the medium firstly making a random translation and a rotation around a random
vector by a random angle. By making a large number of trials the algorithm gets
a value of a three-point correlation function at the point
$(r_1, r_2, \theta)$. The second algorithm takes a precalculated triangle
$(r_1, r_2, \theta)$ from a web pattern and places it in the medium without
rotation, only applying a random translation. This way the algorithm preserves
orientation of triangles stored in the pattern.

Our algorithm fixes $\theta = \frac{pi}{2}$ and does not perform random
rotations or trial triangles. It is sensitive to anisotropicity of the medium
when it is stretched along one of the axes as shown in \cref{fig:ellipses}. The
main advantage of our algorithm is its parallelizability and ease of
implementation.
\begin{figure}[tp]
  \centering
  \includegraphics[width=0.3\linewidth]{images/ellipse-0.png}
  \hfill
  \includegraphics[width=0.3\linewidth]{images/ellipse-45.png}
  \hfill
  \includegraphics[width=0.3\linewidth]{images/ellipse-90.png}
  \vskip\baselineskip
  \includegraphics[width=0.3\linewidth]{images/ellipse-0-s3.png}
  \hfill
  \includegraphics[width=0.3\linewidth]{images/ellipse-45-s3.png}
  \hfill
  \includegraphics[width=0.3\linewidth]{images/ellipse-90-s3.png}
  \caption[]{$S_3$ function for anisotropic media (ellipses). Anisotropicity of
    the medium can be seen on heatmaps of $S_3$ function when the medium is
    stretched along one of the axes.}
  \label{fig:ellipses}
\end{figure}

>>>>

\textcolor{red}{Where to put this?}
We have made a comparison of our algorithm with two algorithms, one of which
proposed by Malmir~et~al \cite{malmir2018} and another proposed by Smith and
Torquato \cite{SMITH1988176}. The first algorithms generates a triangle with
fixed sides $r_1$ and $r_2$ and an angle $\theta$ between them and places it in
the medium firstly making a random translation and a rotation around a random
vector by a random angle. By making a large number of trials the algorithm gets
a value of a three-point correlation function at the point
$(r_1, r_2, \theta)$. The second algorithm takes a precalculated triangle
$(r_1, r_2, \theta)$ from a web-like pattern and places it in the medium without
rotation, only applying a random translation. This way the algorithm preserves
orientation of triangles stored in the pattern.

Our algorithm fixes $\theta = \frac{pi}{2}$ and does not perform random
rotations or trial triangles. It is sensitive to anisotropicity of the medium
when it is stretched along one of the axes as shown in \cref{fig:aniso}. The
main advantage of our algorithm is its parallelizability and ease of
implementation. An equivalent operation for rotation of test triangles is a
rotation of the whole input image which we have implemented in our
CorrelationFunctions.jl package. By applying a rotation to the input first we
made a rest of the algorithm cache-friendly by avoiding random memory access.
\begin{figure}[tp]
  \centering
  \includegraphics[width=0.3\linewidth]{images/aniso.png}
  \hfill
  \includegraphics[width=0.3\linewidth]{images/aniso-s3.png}
  \hfill
  \includegraphics[width=0.3\linewidth]{images/aniso-s3-avg.png}
  \caption[]{$S_3$ function for anisotropic media (on the left) elongated along
    the axis $Y$. Anisotropicity of the medium can be seen on a heatmap of $S_3$
    function (in the middle). An average of 10 $S_3$ evaluations of the medium
    rotated by a random angle is on the right.}
  \label{fig:aniso}
\end{figure}
